PPM-S

### 2020-04-11 docs/index.Rmd
Review changes and add github activity feed to index.

---
title: "PPM-S"
csl: "../input/bib/apa6.csl"
bibliography: "../input/bib/zlibrary.bib"
author: " "
output:
    html_document:
        smart: false
---

@@

>>>>

---
title: "PPM-S"
csl: "../input/bib/apa6.csl"
bibliography: "../input/bib/zlibrary.bib"
author: " "
output:
    html_document:
        smart: false
        includes:
          in_header: head_github-activity.html
---

@@

### Reproducibility and documentation

The repository of the project in Github is structured according to the [IPO reproducibility protocol](https://juancarloscastillo.github.io/ipo/).

<br>

## [Github activity feed](https://github.com/juancarloscastillo/github-activity)

<div id="feed"></div>

<br>
